Discriminative Sensing Based on Signal Processing

### 2017-10-21 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
related works for pca

The identification of the most significative information for one problem is referred to as feature selection by the signal processing and data mining areas, as well as it can be formulated as a principal component problem, which is a widely adopted signal processing technique. Feature selection aims to select a subset of relevant information from a larger dataset, in order to improve: data visualization and data understanding, storage requirements, dimensionality, processing time, discriminative sensing, and to overcome overfitting problems to improve prediction and classification performance \cite{chandrashekar2014survey}.

@@

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) and RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Resusts show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

...

@@

@@

@@

@@

>>>>

The identification of the most significative information for one problem is referred to as feature selection by the signal processing and data mining areas, as well as it can be formulated as a principal component problem, which is a widely adopted signal processing technique for data visualization and feature extraction. Feature selection aims to select a subset of relevant information from a larger dataset, in order to improve: data visualization and data understanding, storage requirements, dimensionality, processing time, discriminative sensing, and to overcome overfitting problems to improve prediction and classification performance \cite{chandrashekar2014survey}.

@@

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminative analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

Fink and Sukenik \cite{fink2011effect} explore the relationships among IT infrastructure capability and IT business value using PCA applied to all indicators of their study, resulting into 11 factors, with the first factor accounting for only 27.9\% of the variance. This technique was used because the PCA extracts orthogonal factors that overcome the problem of multicollinearity.

Ramos \emph{et al} \cite{ramos2016information} propose an overview regarding the evolution of scientific research on IT Governance critical success factors within the domain of public administration. By means of bibliometric analysis it was investigated seminal works regarding this theme, considering the characteristic key words found during our analysis. The results present 64 critical success factors with high impact on IT governance.

Guyon \emph{et al} \cite{guyon2002gene} propose a method of gene selection utilizing Support Vector Machine methods based on Recursive Feature Elimination (RFE) and demonstrate that the selected genes yield better classification performance and are biologically relevant to cancer.  The proposed method eliminates gene redundancy automatically and yields better and more compact gene subsets.

@@

In order to audit IT governance of public institutions, the Federal Court of Accounts (TCU, in Portuguese) surveys data of IT practices from these institutions. Although these surveys started in 2007 with 39 questions, nowadays they contain more than 100 questions that allow TCU to rank these institutions by their IT governance index.

@@

To the best of our knowledge, we are the first to propose a critical factors analysis based on PCA for visual discriminative analysis and based on RFE combined with SVM for CSF identification.

@@

PCA combines similar (correlated) attributes and creates new ones. Superior to original attributes.

Feature selection doesn't combine attributes. Just evaluates their quality, predictive power and select the best set.

Benefit in PCA is that combination of N attributes is better than any individual attribute. Disadvantage is in harder explanation what exactly that PCA component means.

@@

Recursive feature elimination is based on the idea to repeatedly construct a model (for example an SVM or a regression model) and choose either the best or worst performing feature (for example based on coefficients), setting the feature aside and then repeating the process with the rest of the features. This process is applied until all features in the dataset are exhausted. Features are then ranked according to when they were eliminated. As such, it is a greedy optimization for finding the best performing subset of features.

The stability of RFE depends heavily on the type of model that is used for feature ranking at each iteration. Just as non-regularized regression can be unstable, so can RFE when utilizing it, while using ridge regression can provide more stable results.

%Given an external estimator that assigns weights to features e.g., the coefficients of a linear model, recursive feature elimination RFE is to select features by recursively considering smaller and smaller sets of features. First, the estimator is trained on the initial set of features and the importance of each feature is obtained either through a coef attribute or through a feature_importances attribute. Then, the least important features are pruned from current set of features.That procedure is recursively repeated on the pruned set until the desired number of features to select is eventually reached.

### 2017-10-21 docs/thesis/chapters/5_tensor_dl/tensor_dl.tex
related works for pca

@@

>>>>

Compressed sensing (also known as compressive sensing, compressive sampling, or sparse sampling) is a signal processing technique for efficiently acquiring and reconstructing a signal, by finding solutions to underdetermined linear systems. This is based on the principle that, through optimization, the sparsity of a signal can be exploited to recover it from far fewer samples than required by the Shannon-Nyquist sampling theorem. There are two conditions under which recovery is possible.[1] The first one is sparsity which requires the signal to be sparse in some domain. The second one is incoherence which is applied through the isometric property which is sufficient for sparse signals.[2][3]

A common goal of the engineering field of signal processing is to reconstruct a signal from a series of sampling measurements. In general, this task is impossible because there is no way to reconstruct a signal during the times that the signal is not measured.

Around 2004, Emmanuel Candès, Terence Tao, and David Donoho proved that given knowledge about a signal's sparsity, the signal may be reconstructed with even fewer samples than the sampling theorem requires.[4][5] This idea is the basis of compressed sensing. 	https://www.wired.com/2008/03/engineers-test-highly-accurate-face-recognition/

Sparse dictionary learning is a representation learning method which aims at finding a sparse representation of the input data (also known as sparse coding) in the form of a linear combination of basic elements as well as those basic elements themselves. These elements are called atoms and they compose a dictionary. Atoms in the dictionary are not required to be orthogonal, and they may be an over-complete spanning set. This problem setup also allows the dimensionality of the signals being represented to be higher than the one of the signals being observed. The above two properties lead to having seemingly redundant atoms that allow multiple representations of the same signal but also provide an improvement in sparsity and flexibility of the representation.

sparse coding is a sparse representation of one data in the form of a linear combination of basic elements. These elements are called atoms and they compose a dictionary.

One of the key principles of dictionary learning is that the dictionary has to be inferred from the input data. The emergence of sparse dictionary learning methods was stimulated by the fact that in signal processing one typically wants to represent the input data using as few components as possible. Before this approach the general practice was to use predefined dictionaries (such as fourier or wavelet transforms). However, in certain cases a dictionary that is trained to fit the input data can significantly improve the sparsity, which has applications in data decomposition, compression and analysis and has been used in the fields of image denoising and classification, video and audio processing. Sparsity and overcomplete dictionaries have immense applications in image compression, image fusion and inpainting.

@@

Receiver Operating Characteristic Curve (ROC curve) http://www.chioka.in/differences-between-roc-auc-and-pr-auc/

A ROC curve is plotting True Positive Rate (TPR) against False Positive Rate (FPR).

TPR is defined as:

tpr-formula

FPR is defined as:

fpr-formula

where TP = true positive, TN = true negative, FP = false positive, FN = false negative.

A typical ROC curve looks like this, which shows two ROC curves for Algorithm 1 and Algorithm 2.

sample-ROC-curve

The goal is to have a model be at the upper left corner, which is basically getting no false positives – a perfect classifier.

The receiver operating characteristic area under curve (ROC AUC) is just the area under the ROC curve. The higher it is, the better the model is.

Precision Recall Curve (PR Curve)
A PR curve is plotting Precision against Recall.

Precision is defined as:

precision-formula

Recall is defined as:

recall-formulaA typical PR curve looks like this, which shows two PR curves for Algorithm 1 and Algorithm 2.

sample-PR-curve

The goal is to have a model be at the upper right corner, which is basically getting only the true positives with no false positives and no false negatives – a perfect classifier.

The precision recall area under curve (PR AUC) is just the area under the PR curve. The higher it is, the better the model is.

Differences between the ROC AUC and PR AUC
Randy has given a great explanation here, plus a little of my understanding.

Since PR does not account for true negatives (as TN is not a component of either Precision or Recall), or there are many more negatives than positives (a characteristic of class imbalance problem), use PR. If not, use ROC.
